Component response rate variation underlies the stability of complex systems

### 2020-03-21 notebook/ms.Rmd
Fix an error about k in small world networks, which was actually parameterised as S/12, not S/2

Small-world networks were constructed using the method of Watts and Strogatz [@Watts1998]. First, a regular network [@Watts1998] was created such that components were arranged in a circle. Each component was initially set to interact with its $k/2$ closest neighbouring components on each side, where $k$ was an even natural number (e.g., for $k = 2$ the regular network forms a ring in which each component interacts with its two adjacent neighbours; see Supplemental Material for examples). Each interaction between a focal component and its neighbour was then removed and replaced with with a probability of $\beta$. In replacement, a new component was randomly selected to interact with the focal component; selection was done with equal probability among all but the focal component. The resulting small-world network was represented by a square $S \times S$ binary matrix $\mathbf{B}$ in which 1s represented interactions between components and 0s represented the absence of an interaction. A new random matrix $\mathbf{J}$ was then generated with elements $J_{ij}$ sampled i.i.d. from $\mathcal{N}(0, 0.4)$. To build the interaction matrix $\mathbf{A}$, I used element-wise multiplication $\mathbf{A} = \mathbf{J} \odot \mathbf{B}$, then set $diag(\mathbf{A}) = -1$. I set $k = S/2$ and simulated small-world networks across all combinations of $S = \{24, 48, 72, 96, 120, 144, 168\}$ and $\beta = \{0, 0.01, 0.1, 0.25, 1\}$.

>>>>

Small-world networks were constructed using the method of Watts and Strogatz [@Watts1998]. First, a regular network [@Watts1998] was created such that components were arranged in a circle. Each component was initially set to interact with its $k/2$ closest neighbouring components on each side, where $k$ was an even natural number (e.g., for $k = 2$ the regular network forms a ring in which each component interacts with its two adjacent neighbours; see Supplemental Material for examples). Each interaction between a focal component and its neighbour was then removed and replaced with with a probability of $\beta$. In replacement, a new component was randomly selected to interact with the focal component; selection was done with equal probability among all but the focal component. The resulting small-world network was represented by a square $S \times S$ binary matrix $\mathbf{B}$ in which 1s represented interactions between components and 0s represented the absence of an interaction. A new random matrix $\mathbf{J}$ was then generated with elements $J_{ij}$ sampled i.i.d. from $\mathcal{N}(0, 0.4)$. To build the interaction matrix $\mathbf{A}$, I used element-wise multiplication $\mathbf{A} = \mathbf{J} \odot \mathbf{B}$, then set $diag(\mathbf{A}) = -1$. I set $k = S/12$ and simulated small-world networks across all combinations of $S = \{24, 48, 72, 96, 120, 144, 168\}$ and $\beta = \{0, 0.01, 0.1, 0.25, 1\}$.

### 2020-03-21 notebook/ms.tex
Rearrange the results files so that the manuscript calls them from the inst Rpackage folder
Minor tweak to the files being read into the main text
Fix an error about k in small world networks, which was actually parameterised as S/12, not S/2

Small-world networks were constructed using the method of Watts and
Strogatz\textsuperscript{\protect\hyperlink{ref-Watts1998}{15}}. First,
a regular network\textsuperscript{\protect\hyperlink{ref-Watts1998}{15}}
was created such that components were arranged in a circle. Each
component was initially set to interact with its \(k/2\) closest
neighbouring components on each side, where \(k\) was an even natural
number (e.g., for \(k = 2\) the regular network forms a ring in which
each component interacts with its two adjacent neighbours; see
Supplemental Material for examples). Each interaction between a focal
component and its neighbour was then removed and replaced with with a
probability of \(\beta\). In replacement, a new component was randomly
selected to interact with the focal component; selection was done with
equal probability among all but the focal component. The resulting
small-world network was represented by a square \(S \times S\) binary
matrix \(\mathbf{B}\) in which 1s represented interactions between
components and 0s represented the absence of an interaction. A new
random matrix \(\mathbf{J}\) was then generated with elements \(J_{ij}\)
sampled i.i.d. from \(\mathcal{N}(0, 0.4)\). To build the interaction
matrix \(\mathbf{A}\), I used element-wise multiplication
\(\mathbf{A} = \mathbf{J} \odot \mathbf{B}\), then set
\(diag(\mathbf{A}) = -1\). I set \(k = S/2\) and simulated small-world
networks across all combinations of
\(S = \{24, 48, 72, 96, 120, 144, 168\}\) and
\(\beta = \{0, 0.01, 0.1, 0.25, 1\}\).

@@

\includegraphics{ms_files/figure-latex/unnamed-chunk-9-1.pdf}

@@

>>>>

Small-world networks were constructed using the method of Watts and
Strogatz\textsuperscript{\protect\hyperlink{ref-Watts1998}{15}}. First,
a regular network\textsuperscript{\protect\hyperlink{ref-Watts1998}{15}}
was created such that components were arranged in a circle. Each
component was initially set to interact with its \(k/2\) closest
neighbouring components on each side, where \(k\) was an even natural
number (e.g., for \(k = 2\) the regular network forms a ring in which
each component interacts with its two adjacent neighbours; see
Supplemental Material for examples). Each interaction between a focal
component and its neighbour was then removed and replaced with with a
probability of \(\beta\). In replacement, a new component was randomly
selected to interact with the focal component; selection was done with
equal probability among all but the focal component. The resulting
small-world network was represented by a square \(S \times S\) binary
matrix \(\mathbf{B}\) in which 1s represented interactions between
components and 0s represented the absence of an interaction. A new
random matrix \(\mathbf{J}\) was then generated with elements \(J_{ij}\)
sampled i.i.d. from \(\mathcal{N}(0, 0.4)\). To build the interaction
matrix \(\mathbf{A}\), I used element-wise multiplication
\(\mathbf{A} = \mathbf{J} \odot \mathbf{B}\), then set
\(diag(\mathbf{A}) = -1\). I set \(k = S/12\) and simulated small-world
networks across all combinations of
\(S = \{24, 48, 72, 96, 120, 144, 168\}\) and
\(\beta = \{0, 0.01, 0.1, 0.25, 1\}\).

@@

\includegraphics{ms_files/figure-latex/unnamed-chunk-8-1.pdf}

@@

\includegraphics{ms_files/figure-latex/unnamed-chunk-11-1.pdf}
